---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# standby

<!-- badges: start -->
<!-- [![R-CMD-check](https://github.com/rsquaredacademy/standby/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rsquaredacademy/standby/actions/workflows/R-CMD-check.yaml) [![status](https://tinyverse.netlify.com/badge/standby)](https://CRAN.R-project.org/package=standby) -->
<!-- [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable) -->
<!-- badges: end -->

Loading screens for Shiny

## Installation

You can install the development version of standby from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/standby")
```

## Usage

<!-- Below is a simple example of the package, visit the [website](https://standby.rsquaredacademy.com) for more. -->

## Example

```{r example, eval=FALSE}
library(shiny)
library(standby)

ui <- fluidPage(

  standby::useSpinkit(), # include dependencies
  fluidRow(
    standby::spinkit(plotOutput("plot1")), # wrap output inside loader
    actionButton("render", "Render")
  )

)

server <- function(input, output, session) {

    output$plot1 <- renderPlot({
      input$render
      Sys.sleep(3)
      plot(cars)
    })

}

shinyApp(ui, server)

```

## Details

**standby** offers several types of loaders/spinners. Visit the below websites to learn more:

- [Three Dots](https://github.com/nzbin/three-dots)
- [SpinKit](https://github.com/tobiasahlin/SpinKit)
- [Loading Visualization](https://github.com/RIDICS/Loading-Visualization)
- [CSS Spinners](https://github.com/lukehaas/css-loaders)
- [CSS Loaders](https://github.com/raphaelfabeni/css-loader)

## Inspiration

The following packages served as an inspiration. 

- [shinycssloaders](https://github.com/daattali/shinycssloaders) by [Dean Attali](https://attalitech.com/)
- [waiter](https://github.com/JohnCoene/waiter) by [John Coene](https://john-coene.com/)

## Acknowledgements

We referred to the following books extensively while developing standby and are grateful to the authors for sharing their knowledge with the R/Shiny community:

- [Outstanding User Interfaces with Shiny](https://unleash-shiny.rinterface.com/index.html) by [David Granjon](https://divadnojnarg.github.io/)
- [JavaScript for R](https://book.javascript-for-r.com/) by [John Coene](https://john-coene.com/)

## Getting Help

If you encounter a bug, please file a minimal reproducible example using 
[reprex](https://reprex.tidyverse.org/index.html) on github. For questions and clarifications, 
use [StackOverflow](https://stackoverflow.com/).

## Code of Conduct

Please note that the standby project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
