---
title: "Quick Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

buzz offers several types of alerts, notifications and tooltips. This 
document is a quickstart guide for using buzz in your Shiny applications. 
Let us look at a simple example below:

```{r example, eval=FALSE}
library(shiny)
library(buzz)

ui <- fluidPage(
 
  useToast(), # include dependencies
  actionButton(inputId = "btn",
               label   = "iziToast Demo")
 
)
 
server <- function(input, output, session) {

  observeEvent(input$btn, {
    # display toast notification
    toast("Hey there!", "Thank you for exploring buzz!")
  })
}

shinyApp(ui, server)
```

To use alerts or notifications from **buzz** in your Shiny application, follow the below steps:

- Include the dependencies in the **UI** part of the app using the appropriate
`use*` functions (`useToast()` in the above example).
- Include the corresponding rendering function in the **Server** part of the 
app (`toast()` in the above example).

## Details

The below table displays the dependency and rendering functions along with references:

```{r ref_table, echo=FALSE}
index <- 1:8
dependency <- c("`useAlertify()`", "`useAlertify()`", "`useBootBox()`", "`useMicroTip()`", 
                "`useNS()`", "`useNotify()`", "`useTingle()`", "`useToast()`")
renderer <- c("`alertify_alert()`", "`alertify_notify()`", "`bootBox()`", "`microTip()`",
              "`notice()`", "`notify()`", "`tingle()`", "`toast()`")
reference <- c("https://github.com/MohammadYounes/AlertifyJS",
               "https://github.com/MohammadYounes/AlertifyJS",
               "https://github.com/makeusabrew/bootbox",
               "https://github.com/ghosh/microtip",
               "https://tympanus.net/Development/NotificationStyles/",
               "https://github.com/sciactive/pnotify",
               "https://github.com/robinparisi/tingle",
              "https://github.com/marcelodolza/iziToast")
ref <- data.frame(Index = index, Dependency = dependency, Render = renderer, Reference = reference)
kableExtra::kable(ref)
```

Visit the [documentation](https://buzz.rsquaredacademy.com) to learn how to 
customize the alerts and notifications.