---
title: "Loading Screens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading Screens}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

standby offers several types of loading screens for Shiny apps. This 
document is a quickstart guide for using standby in your Shiny applications. 
Let us look at a simple example below:

```{r example, eval=FALSE}
library(shiny)
library(standby)

ui <- fluidPage(

  standby::useSpinkit(), # include dependencies
  fluidRow(
    standby::spinkit(plotOutput("plot1")), # wrap output inside loader
    actionButton("render", "Render")
  )

)

server <- function(input, output, session) {

    output$plot1 <- renderPlot({
      input$render
      Sys.sleep(3)
      plot(cars)
    })

}

shinyApp(ui, server)
```

To use spinners/loaders from **standby** in your Shiny application, include the 
following in the **UI** part of the app:

- Include the dependencies using the appropriate `use*` functions 
(`useSpinkit()` in the above example).
- Wrap the target output using corresponding rendering function 
(`spinkit()` in the above example).

The below table displays the dependency and rendering functions along with references:

```{r ref_table, echo=FALSE}
index <- 1:5
dependency <- c("`useThreeDots()`", "`useSpinkit()`", "`useVizLoad()`", "`useSpinners()`", 
                "`useLoaders()`")
renderer <- c("`threeDots()`", "`spinkit()`", "`vizLoad()`", "`spinners()`",
              "`loaders()`")
reference <- c("https://github.com/nzbin/three-dots",
               "https://github.com/tobiasahlin/SpinKit",
               "https://github.com/RIDICS/Loading-Visualization",
               "https://github.com/lukehaas/css-loaders",
               "https://github.com/raphaelfabeni/css-loader")
ref <- data.frame(Index = index, Dependency = dependency, Render = renderer, Reference = reference)
kableExtra::kable(ref)
```

Visit the [documentation](https://standby.rsquaredacademy.com) to learn how to 
customize the alerts and notifications.
